---
title: 'Assignment 3: Hadoop, MapReduce, R, and Mahout'
author: "Justin Sallese"
date: "April 22, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##Hive code

  Below are data results that follow the analysis that is provided within chapter 3 of the book Information
Security Analytics: Finding Security Insights, Patterns, and Anomalies in Big Data by  Mark Ryan M. Talabis,
Robert McPherson, I. Miyamoto and Jason L. Martin.

  Situation: The data that has been used is made up of apache combined server log files. The analysis that is to be
done is an analysis of the types of access to the server that the log files have come from. The analysis is to be
done useing the hive program that is running on cloudera quick start VM.


  Below is the results to the hive query whether or not if there was an attack using SQl injection. Below can be 
seen the result in which there was an attack useing SQL injection where the attacker tried to access user names 
and passwords from the database. If this where a proffesional report to a company I, based on the data that is
provided would reccomend furthur defenses to be set up so attacks like the SQL injection would not happen again 
in the future.

[SQL Injection Attack](https://github.com/jsallese/Assignment3/blob/master/cloudera-quickstart-vm-5.10.0-0-vmware-2017-04-21-23-12-56.png)


  Below are the result to the hive query which was checking if there 
where attacks to perform directroy traversal and file inclusion. 
Directroy traversal and file inclusion is when the attackers send 
command are made to give them access to the directories to put, get 
and alter files within the computers database. Below are the result 
of the query which are showing that there where multiple attepts 
that failed (Failure is shown by status codes 404 and 531), but the 
results also show that there where two attepts that where 
succsessful. If this where a proffesional report to a company I, 
based on the data that is provided would reccomend furthur defenses 
to be implemented to prenent directory traversal and file inclusion 
attacks

[Directory Traversal and File inclusion](https://github.com/jsallese/Assignment3/blob/master/cloudera-quickstart-vm-5.10.0-0-vmware-2017-04-21-23-16-13.png)

  Below are the resluts to the hive query search on a Cross Site Request Forgery which pertains
to browsers Javascript alert notice. Attacks such as these are one such attack that uses password phishing
in its attack. As one can see there are results in the data below, though  if this where a where 
a proffesional report to a company I, based on the data that is provided would reccomend furthur defenses
to be made that prevents  Cross Site Request Forgery from happening againm which in turn leaves 
the computer more secure in the long run.

[Cross Site Request Forgery](https://github.com/jsallese/Assignment3/blob/master/cloudera-quickstart-vm-5.10.0-0-vmware-2017-04-21-23-23-37.png)

  Below are the results to the hive query that checks the data on possible command injection 
attacks. These attacks try to disguise commands with HTML URL encoding. As one can see below 
there are results shown within the data.

[Command injection](https://github.com/jsallese/Assignment3/blob/master/cloudera-quickstart-vm-5.10.0-0-vmware-2017-04-21-23-28-39.png)

  Below are the results to the hive query that checks the data on possible MySQL Charset Switch
and MS-SQL DoS Attack. This attack involver atlering a character set that is used for 
functionality of databases and avoiding DDOS attack. As can be seen below there are results 
where the attacker changed the character set gbk_chinese_ci. 

[MySQL Charset Switch and MS-SQL DoS Attack](https://github.com/jsallese/Assignment3/blob/master/cloudera-quickstart-vm-5.10.0-0-vmware-2017-04-21-23-30-20.png)

  Below are the results to the hive query that checks the data on the most failed requests sent
to the server. This data would be able to tell us when the most failed requests happen and 
help us identify the specific host and day which had the most failed access which could 
likely be an attacker. The host with the most accesses should be investigated in the future

[Hosts with the Most Failed Requests](https://github.com/jsallese/Assignment3/blob/master/cloudera-quickstart-vm-5.10.0-0-vmware-2017-04-21-23-47-26.png)

  Below is the results if the hive query which was searching the access logs for bot activity.
Below lists the results and the hits in which the bot was found. Possible defenses in the
future could include verification of access to the apache server. 

[Bot Activity](https://github.com/jsallese/Assignment3/blob/master/cloudera-quickstart-vm-5.10.0-0-vmware-2017-04-21-23-53-41.png)

  Below are the resultsof the Hosts with the Most Failed Requests per Day and per month. This
data can tell us what host to investigate undedr the suspicion of more failed requests, which
can be a sign that the host is an attacker trying to send commands.

[Hosts with the Most Failed Requests per Day ](https://github.com/jsallese/Assignment3/blob/master/cloudera-quickstart-vm-5.10.0-0-vmware-2017-04-22-00-00-34.png)

[Hosts with the Most Failed Requests per Month](https://github.com/jsallese/Assignment3/blob/master/cloudera-quickstart-vm-5.10.0-0-vmware-2017-04-22-00-02-53.png)

  Below are the data results from hive where the data has been calculated as a ratio of failed 
to successful requests as a time series. This data can tell us th yeay and the month where 
the ratio was the highest. These results can tell us what year that should be analysed more 
in depth. As shown wihtin the results the year and month with the highest ratio
[Ratio of Failed to Successful Requests as a Time Series](https://github.com/jsallese/Assignment3/blob/master/cloudera-quickstart-vm-5.10.0-0-vmware-2017-04-22-18-37-45.png)


##R Code of the Ratio of Failed to Successful Requests as a Time Series

  The codeing to the plots below have been taken from
chapter 3 of Information Security Analytics: Finding
Security Insights, Patterns, and Anomalies in Big Data
by  Mark Ryan M. Talabis, Robert McPherson, I. Miyamoto
and Jason L. Martin

```{r, message=FALSE, warning=FALSE}
library(fBasics)
library(readr)
failedRequests <- read.csv("~/Desktop/untitled folder/failedrequestsbyday.csv")

colnames(failedRequests) <- c("Date","FailedRequestsRatio")
stdev <- sd(failedRequests$FailedRequestsRatio) 
avg <- mean(failedRequests$FailedRequestsRatio) 
avgPlus2Stdev <- avg + 2 * stdev 
failedRequests[failedRequests[,2]>avgPlus2Stdev,]

plot(failedRequests[,2],type='l',main="Ratio of Failed 
Server Requests to Successful Requests by Day" 
,xlab="Day",ylab="Ratio of Failed Requests to Successful 
Requests")
lines(rep(avg,length(failedRequests[,2])))
lines(rep(avgPlus2Stdev,length(failedRequests[,2])),lty=2)
legend("topright",c("Average","2 X Standard 
Deviation"),lty=c(1,2))
```

Below is a link to the plot in case the one generated is not to your liking.

[Ratio of Failed Server Requests to Successful Requests by Day](https://github.com/jsallese/Assignment3/blob/master/Ratio%20of%20Failed%20Server%20Requests%20to%20Successful%20Requests%20by%20Day.jpeg)


  Above is a plot of the ratio of failed server requests to
succsesful requests by day.It shows the times in which the
number of requests have exceeded the threshold average.
The three times in which the ratio has exceeded the
threshold is July 24, 2009; September 25, 2009; and
September 28, 2009. Furthur investigation would be needed
on the dates listed to determine if the cause was seasonal or done by other means

```{r}
acfPlot(failedRequests[,2],lag.max=60)
```

Below is a link to the plot in case the one generated is not to your liking.

[Ratio of Failed Server Requests to Successful Requests by Day aggregated further](https://github.com/jsallese/Assignment3/blob/master/Ratio%20of%20Failed%20Server20Requests%20to%20Successful%20Requests%20by%20Day.jpeg)

  The above plot shows an further aggregation to the data of
the ratio of failed server requests to succsesful requests
by day.

##Conclusion

Based on the provided access logs and the analysis that followed the apache server is quite 
vulnrable and is in need of various defenses to defend against furthur attacks. I have learned 
the process in which one can use cloudera and hive to easily sort large amounts of data.


##Works Cited

"Log Files." Log Files - Apache HTTP Server. N.p., n.d. Web. 22 Apr. 2017.

Pig Tutorial (n.d.): n. pag. Apache Software Foundation. Web. 22 Apr. 2017.

Talabis, Mark , Robert Mcspherson, I. Miyamoto, and Jason Martin. "Information Security Analytics." 
Google Books. N.p., n.d. Web. 22 Apr. 2017.


